Paper 3 - Causal Roadmap

### 2023-03-09 docs/causal_roadmap.qmd
Added unique file for acronyms and authors. Fixed problem of list of acronyms before TOC

---
title: "Paper 3 - Causal Roadmap"
keywords:
  - Causal Inference
  - Epidemiology
  - Triangulation
  - Modified Treatment Policy
  - Mendelian Randomization
  - Metabolomics
  - Endocrine Disrupting Chemicals
  - Neurodevelopment
  - Neurobehavior
author:
  - name: "Lorenzo Fabbri"
    number: 1
    email: lorenzo.fabbri@isglobal.org
    orcid: 0000-0003-3031-322X
    attributes:
      corresponding: true
    affiliations:
      - ref: isg
      - ref: upf
affiliations:
  - id: isg
    name: Barcelona Institute for Global Health (ISGlobal)
    city: Barcelona
    state: Spain
  - id: upf
    name: Pompeu Fabra University
    city: Barcelona
    state: Spain
format:
  pdf:
    pdf-engine: pdflatex
    number-sections: true
    toc: true
    margin-left: 15mm
    margin-right: 15mm
    margin-bottom: 20mm
    margin-top: 15mm
    include-in-header:
      - \usepackage{rotating}
      - \usepackage{float}
      - \usepackage{typearea}
    pandoc_args:
      - !expr acronymsdown::add_filter()
bibliography: ../../../PhD.bib
link-citations: true
linkcolor: blue
execute:
  echo: false
editor_options: 
  chunk_output_type: console
filters:
  - /home/lorenzo/R/x86_64-pc-linux-gnu-library/4.1/acronymsdown/parse-acronyms.lua
acronyms:
  fromfile: ../../../all_phd/acronyms.yml
  insert_links: false
  sorting: alphabetical
---

>>>>

---
title: "Paper 3 - Causal Roadmap"
keywords:
  - Causal Inference
  - Epidemiology
  - Triangulation
  - Modified Treatment Policy
  - Mendelian Randomization
  - Metabolomics
  - Endocrine Disrupting Chemicals
  - Neurodevelopment
  - Neurobehavior
metadata-files:
  - ../../../all_phd/authors.yml
format:
  pdf:
    pdf-engine: pdflatex
    number-sections: true
    toc: false
    margin-left: 15mm
    margin-right: 15mm
    margin-bottom: 20mm
    margin-top: 15mm
    include-in-header:
      - \usepackage{rotating}
      - \usepackage{float}
      - \usepackage{typearea}
    pandoc_args:
      - !expr acronymsdown::add_filter()
bibliography: ../../../PhD.bib
link-citations: true
linkcolor: blue
execute:
  echo: false
editor_options: 
  chunk_output_type: console
filters:
  - /home/lorenzo/R/x86_64-pc-linux-gnu-library/4.1/acronymsdown/parse-acronyms.lua
  - ../../../all_phd/scholarly-metadata.lua
  - ../../../all_phd/author-info-blocks.lua
acronyms:
  fromfile: ../../../all_phd/acronyms.yml
  insert_links: false
  insert_loa: false
  sorting: alphabetical
---

```{=latex}
\setcounter{tocdepth}{4}
\tableofcontents
```

\printacronyms
